---
title: "Midterm"
author: "Monika Lind"
date: "4/30/2019"
output: html_document
---

```{r library, message = FALSE, warning = FALSE}
library(tidyverse)
library(glue)
library(rio)
library(janitor)
# install.packages("pracma")
library(pracma)
```

# Part A  

## 1.  

```{r}
download_file <- function(year) {
    link <- glue::glue("https://www.oregon.gov/ode/educator-resources/assessment/TestResults20{year}/pagr_schools_ela_raceethnicity_{year-1}{year}.xlsx")
    rio::import(link, setclass = "tibble", na = c("-", "--", "*"))
}

d <- map_df(seq(15, 18, 1), download_file)

tidy <- d %>% 
  clean_names() %>% 
  filter(student_group == "White" | student_group == "Hispanic/Latino") %>% 
  select(1, 3, 5, 7, 8, 11, 13, 15, 17) %>% 
  gather("level", "n", -1:-5) %>% 
  mutate(level = parse_number(level)) %>% 
#  filter(n != is.na(n))
  filter(!is.na(n)) %>% 
  arrange(academic_year, district, student_group, grade_level)
head(tidy)
```

***  

## 2.  

```{r}
tidy2 <- tidy %>% 
  arrange(school, student_group, grade_level, academic_year, level) %>% 
  mutate(student_group = tolower(student_group),
         student_group = str_replace_all(student_group, "/", "_")) %>% 
  group_by(school, student_group, grade_level, academic_year) %>% 
# Why does it matter what order you put the group_by in?
  mutate(cn = cumsum(n))
head(tidy2)
```

***  

## 3.  
```{r}
tidy3 <- tidy2 %>% 
  select(-7) %>% 
  spread(student_group, cn) %>% 
  filter(!is.na(hispanic_latino),
         !is.na(white))
head(tidy3)
```

***  

# Part B  

## 1.  
(10 points) Estimate an achievement gap effect size for every school in the state that reported data on both student groups (i.e., using the data we created above), for each grade level in each academic year.  

```{r}
gap <- function(data, ref, foc) {
    x <- data[[ref]]
    y <- data[[foc]]
    auc <- pracma::trapz(y / y[length(x)],
                         x / x[length(x)])
    sqrt(2)*qnorm(auc)
}

tidy4 <- tidy3 %>% 
  group_by(school, grade_level, academic_year, district) %>% 
  nest() %>% 
  mutate(effect = map_dbl(data, gap, "white", "hispanic_latino"))
head(tidy4)
```

***  

## 2.  
(10 points) The plot below shows the achievement gap estimates for one school by grade in Ashland School District during the 2017-18 school year. Produce a similar plot to the below (noting the school, academic year, and school district) for each of the first 100 unique school/year/district combinations. Hint - you’ll want to use your effect size data from from the previous question, nest it, then apply slice(1:100). Note that the only reason I’m asking you to slice the data frame is just to reduce run time. In reality, you would do this for all school/year/district combinations.  
```{r}
tidy5 <- tidy4 %>% 
  select(-5) %>% 
  group_by(school, academic_year, district) %>% 
  nest() %>% 
  slice(1:100) %>% 
  mutate(plots = pmap(list(data, school, district, academic_year), 
                      ~ggplot(..1, aes(grade_level, effect, fill = effect)) +
                          geom_col() +
                          coord_flip() +
                          labs(title = glue("Achievement Gap Estimates: {..2}"),
                               subtitle = "Students coded as White compared to students coded as Hispanic/Latino",
                               caption = glue("{..4} School year, {..3} School District, Oregon"))))
head(tidy5)
```

***  

## 3.  
(10 points) Save the plots into a “plots” directory. Make sure the file names are meaningful.  
```{r}
save_plots <- tidy5 %>% 
  mutate(file_names = glue("{school}_{academic_year}_{district}_ach-gap"))

fs::dir_create(here::here("plots"))

paths <- here::here("plots", glue("{save_plots$file_names}.png"))

walk2(paths, save_plots$plots, ggsave,
      width = 9.5, 
      height = 6.5,
      dpi = 500)
```







